Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-13 papers/B1555_EdgeOn/B1555_letter.tex
Change in paragraph order in Discussion

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. Discrepency between numerical simulation and observation within the local universe gives two possible interpretations: an alternative structure formation model or small sample arise from nowaday observation. Difficulties emerge in direct detection when searching beyond the Local Group. Until now, most of known satellites are at high mass end in the mass function. However, the gravitational perturbations from substructures can cause detectable change in surface brightness among lensed images. This makes gravitational lensing a powerful tool for searching substructures. Flux ratio anomalies in strongly lensed quasars become a sign of existence of subhalo. Total mass of substructures can be derived from their gravitational effects and also give direct measurement of mass function which avoid making assumptions on baryonic matter distribution assoociated with dark matter.

In the most of discussions upon multiple image lensed quasars, flux ratio anomalies are brought only by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential (in ideal case, i.e. no dust extinction, micro lensing, scattering etc.). Numerical simulations have examined this idea with known flux anomalous lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of these radio flux anomalies. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure originated flux anomaly, including our target B1555+375. They conclude the failure on B1555+375 with improper lens model. Their result can be supported by SHARP $K^{\prime}$ band image, which an edge-on disk lies across between the radio merging double A \& B. A more complex lens model (e.g. include an exponential disk) must be considered for B1555+375.

In part 3, we present new lens models of B1555+375. The most significant difference comparing to previous modelling is a new edge-on disk component. With a bulge plus an edge-on disk, our models fairly match the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail. Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}. Our successful modelling indicates that the structure from lens galaxy itself causes the flux ratio anomalies in B1555+375. An edge-on disk with high ellipcity well explains the observed flux ratios without the presense of substructrues. This breaks the idea that in strongly lensed quasars, radio flux ratio anomalies are most likely originated from substructure perturbations. It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures. Our discover shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in the system. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. To gather correct statistics, one must fully consider non-substructure effects. Otherwise, possible ``false'' substructures detected by flux anomalies can serverly biased the data analysis. Even with real substructures presence, lens galaxy structure can still dominate the flux anomalous phenomenon and have impact on estimated mass and also other derived properties. We would like to draw attention on this non-substructure effect brought by a large, high ellipcity edge-on disk. For precise measurement on substurcture population, mass function, and any derived properties from strong lensed flux anomalous systems, careful estimation on non-substructure effects are important.

Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars. Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With an high ellipcity edge-on disk, our new lens models well explain the flux ratio anomalies. Lack of knowledge on lens galaxy can lead to an improper lens model and thus cause bias to statics and derived properties among substructure detection. With the first system being analyzed and shown that an edge-on disk from lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\

>>>>

\section{Discussion}

We present new lens models of B1555+375. With the new imaging from SHARP $K^{\prime}$ band, the most significant difference comparing to previous modelling is a new edge-on disk component. With a bulge plus an edge-on disk, our models fairly match to the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail. Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}. Our successful modelling indicates that the structure from lens galaxy itself causes the flux ratio anomalies in B1555+375. An edge-on disk with high ellipcity well explains the observed flux ratios without the presense of substructrues. This breaks the idea that in strongly lensed quasars, radio flux ratio anomalies are most likely originated from substructure perturbations. It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures. Our discovery shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomena in the strongly lensed system.

The abundance of substructures within galaxy-size haloes has been an undetermined problem in structure formation studies. Discrepencies between numerical simulations and observations within the local universe gives two possible interpretations: an alternative structure formation model or a small sample set from nowaday observations. Difficulties emerge in direct detection when searching beyond the Local Group. Until now, most of known satellites are at high mass end in the mass function. However, the gravitational perturbation from substructures can cause detectable change in surface brightness among lensed images. This makes gravitational lensing a powerful tool for searching substructures. Flux ratio anomalies in strongly lensed quasars become a sign of existence of subhaloes. Total mass of substructures can be derived from their gravitational effects and also give direct measurement of mass function, avoid making assumptions on baryonic matter distribution assoociated with dark matter.

Given the assumption that lens galaxy has smooth gravitational potential, only substructure perturbations can cause flux ratio anomalies (in ideal case, i.e. no dust extinction, micro lensing, scattering etc.). Numerical simulations demostrate this idea with known flux anomalous lensed quasars. In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalies. By adding subhaloes on to those systems, only one out of six lens systems reproduce the flux anomalies. The rest of them are unlikely to have substructure originated flux anomalies, including our target B1555+375. \citet{Xu14} conclude the failure on B1555+375 due to improper lens models. This result supports our discovery in both observation and lens modelling, that an edge-on disk lies  between the radio merging double explain its flux ratio anomaly.

From the successful modelling of B1555+375,  we expect more flux anomalous systems requiring complex lens models (e.g. include an exponential disk), rather than just assuming smooth potential. Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. It is important to fully consider non-substructure effects before any statistical analysis .Otherwise, possible ``false'' substructures detected by flux anomalies can serverly bias the data analysis. Even with real substructures presence, the lens galaxy structure can still dominate flux anomalous phenomena and impacts on estimated mass and also other derived properties. We would like to draw attention to this non-substructure effect caused by a large, high ellipcity edge-on disk. For precise measurements on substurcture population, mass function, and any derived properties from strong lensed flux anomalous systems, it is crucial to have careful estimation on non-substructure effects.

Our results also show that multi-wavelength imagimg is helpful to explore flux anomalous lensed quasars. Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With an high ellipcity edge-on disk, our new lens models adequately explain the flux ratio anomaly. Lack of knowledge of the lens galaxies can lead to improper lens modelling and bias to statistics among substructure detection. With the first system analyzing and showing that an edge-on disk from the lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. An edge-on disk structure may also able to expalin the flux ratio anomalies of these systems.\\
